% --------------------------------------------------------------
% If you need to add a package or a command, please add a
% comment explaining what it's for
% --------------------------------------------------------------
\documentclass[11pt, titlepage]{article}

\usepackage[margin=1in]{geometry}
\usepackage[strict]{changepage}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{mhchem}
\usepackage{siunitx}
\usepackage{wrapfig, booktabs}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{commath}
\usepackage{amsmath}
\usepackage[hang]{footmisc}
\usepackage{multicol}
\usepackage{amsfonts}
\usepackage{mathrsfs}

\usepackage{tabto}	%for using \tab

% --------------------------------------------------------------
%                         Title Page Info
% --------------------------------------------------------------
\newcommand{\className}{CS 3450}	%for footer
\newcommand{\footerName}{PIP} 		%for footer
\author{Brandon Smith, Nieka Gutenberger, Joseph Coppin, Ryan Frazier, Trevor Jewkes}
\title{Procedure Implementation Plan}
\date{\today}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\cfoot{\className\ -- \footerName}

\usepackage{sectsty}
\setlength{\headheight}{14pt}


\begin{document}
	\maketitle
    \setcounter{tocdepth}{1}
% --------------------------------------------------------------
%                         Proposal Section	-finish requirements section
% --------------------------------------------------------------    
\section{Proposal}    
    
    \subsection{Requirements}
    
    The end goal of the team is to write a Graphical User Interface game which allows the user to play one of two card games.  The user will open the program and choose between Hearts or Spades.  The user will be presented with a gameboard and options to play. 
    
    \par should be clear, should be able to be measured\\
    should be the same over time\\
    shouldn't get overconstrained\\
    
% --------------------------------------------------------------
%                         Structure Section 	still need to write brief overview of
%												each position
% --------------------------------------------------------------
    \section{Structure}
    	Each person in the team has been assigned as the head for a specific role.  		Each role is described briefly as follows:
    
    \subsection{Manager} 
	    Trevor Jewkes
    	\begin{itemize}
    		\item In charge of GitHub account
    		\item Will turn in final versions for group
    		\item In charge of code compilation and merge conflicts
    	\end{itemize}
   
    \subsection{Documentation}
	    Joe Coppin
    	\begin{itemize}
    		\item Writes rough drafts of all papers and submit for peer review
    		\item Writes final draft of all papers and pushes them to GitHub account for Manager to submit
    		\item Head person over documents
    	\end{itemize}
   		
    \subsection{Design}
		Nieka Gutenberger
		\begin{itemize}
			\item In charge of GUI and interface
    		\item Will oversee looks and game design
    		\item will take minutes from meetings and distribute to team members
		\end{itemize}
    	
    \subsection{Testing}
		Ryan Frazier
		\begin{itemize}
			\item Initially gets testing software up and running on GitHub
  		  	\item Writes tests and helps others write tests
    		\item Reviews tests and makes sure they are adequate
    		\item Test tech support
		\end{itemize}
   
    \subsection{Scheduling and Mediation}
	    Brandon Smith
   		\begin{itemize}
    		\item In charge of scheduling and time management
    		\item Workload Balance
    		\item Maintains as even as possible workload balance between team members
    		\item Debate Moderator!
		\end{itemize}
             
     \subsection{*note}
     	Each team member is expected to contribute to the project as needed, meaning there is no defined end to any team members' duties.  It is the responsibility of each team member to communicate their needs to the team Manager and the head of Scheduling and Mediation in order to allow all team members to be able to contribute and help in a timely manner.
% --------------------------------------------------------------
%                         Procedures Section
% --------------------------------------------------------------
    \section{Procedures}
    	\tab brief overview of procedures
    \subsection{Code Reviews}
   		\subsubsection{Conflict Resolution Plan}
        
        \begin{enumerate}
		\item Make suggestion for change to the person who's work is subject to be 	changed
        \item if two cannot come to an agreement the discussion goes to group for 	decision
        \item If group cannot come to a decision, the Team Leader for the section will have final say in decision
		\end{enumerate}
    
    \subsubsection{Readability} 
	    Each section of code written will be reviewed by at least one other team member before being added to the project.  In event of disputes or questions, the conflict resolution plan will be utilized.
    \subsubsection{Reusability}
	    It is the goal of the team to be specific enough code to solve a problem effectively while being general enough that branching out is feasible and well withing the reach of the team in cases of customer requirements.
    \subsubsection{Improvements}
    
    \subsubsection{Bugs} 
   	
    	Take similarly to conflict resolution.  Need to make sure each person in group agrees to solution to bug (unless head makes decision).
    
    \subsection{Styles and Conventions}
    	The team will follow the Google C++ style guide.
    
    \subsection{Testing Framework}
    	Catch Framework??
    
% --------------------------------------------------------------
%                         Schedule Section	--need this part bad.
% --------------------------------------------------------------    
    \section{Schedule}
    
    
% --------------------------------------------------------------
%                         Risks Section	--this will come with the schedule
% --------------------------------------------------------------    
    \section{Risks}
    
\end{document}