\documentclass[11pt, titlepage]{article}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{tabto}	%for using \tab

% --------------------------------------------------------------
%                         Title Page Info
% --------------------------------------------------------------
\newcommand{\className}{CS 3450}	%for footer
\newcommand{\footerName}{SRS} 		%for footer
\author{Brandon Smith, Nieka Gutenberger, Joseph Coppin, Ryan Frazier, Trevor Jewkes}
\title{System Requirements Specifications}
\date{\today}

\pagestyle{fancy}
\rhead{\thepage}
\cfoot{\className\ -- \footerName}

\usepackage{sectsty}
\setlength{\headheight}{14pt}


\begin{document}
	\maketitle
	\setcounter{tocdepth}{1}
	% --------------------------------------------------------------
	%                         Proposal Section
	% --------------------------------------------------------------
	\section{Functionality}
		Client-Server program that allows client to play card games against other humans or against a computer.
	\begin{itemize}
		\item Client can connect to a game and play.
		\item Client may choose between Hearts and Spades.
		\item Client can play without other human players
		\item AI plays correct game
		\item AI makes legal moves
		\item Menu to choose options
			\begin{itemize}
			\item exit game
			\item see past move
			\end{itemize}
	\end{itemize}
	
	\section{Usabiltiy}
		\begin{itemize}
			\item  Be able to choose game to play
			\begin{itemize}
				\item change game options
				\item change number of players
			\end{itemize}
			\item User can view GUI
			\item User can login
			\begin{itemize}
				\item Make new user
				\item Create username
				\item Make password, use password
				\item Change password
				\item Successfully login 
			\end{itemize}
			\item User can view and access menu
			\item User can play appropriate game play
			\item User can quit game (in fit of rage)
			\item User experiences correct end game sequence
			
		\end{itemize}
	\section{Reliabilty}
		\begin{itemize}
			\item Game logic, rules and cards all function in an appropriate manner and as expected.
			\item Abrupt errors will be handled so that user is not affected by other player disconnection.
		\end{itemize}
	\section{Performance}
	\begin{itemize}
		\item Program handles player and AI disconnection from game gracefully.
	\end{itemize}
	\section{Supportability}
		\begin{itemize}
			\item Unit tests for all functions will be included for source code.
			\item Game instructions will be included in program
			\item Game development supported through Dec 16, 2016.
		\end{itemize}
	\section{+}
		\subsection{Design Constraints}
			\begin{itemize}
				\item Team will use wxWidgets 3.1.0 (www.wxwidgets.org) as the GUI library for client side software.
				\item Boost version 1.62.0 (www.boost.org) will be used as additional libraries for the code.
			\end{itemize}			
		\subsection{Implementation Contraints}
			\begin{itemize}
				\item Group standards (as set forth in PIP) will be adhered to.
				\item Project will be built with externpro (https://github.com/smanders/externpro) and cmake (https://cmake.org).
			\end{itemize}
		\subsection{Interface Constraints}
			\begin{itemize}
				\item Network compatibilty with other groups is necessary for gameplay between servers.
				\item Each client must be able to work with all other servers.
			\end{itemize}
		\subsection{Physical Constraints}
			\begin{itemize}
				\item Software will be depoyable on Linux and Windows distributions.
				\begin{itemize}
					\item At current time, Mac systems are unable to use the mandated externpro build.
				\end{itemize}
			\end{itemize}
			
		
\end{document}
